\documentclass{cshwk}

\begin{document}

\title{HW \#2, Chapter 2}

\maketitle

\section*{Problem 2. Chapter 2 P8.}
Referring to Problem P7, suppose the HTML file references eight very small objects on the same server. Neglecting transmission times, how much time elapses with
\begin{itemize}
    \item[a.] Non-persistent HTTP with no parallel TCP connections?
    \item[b.] Non-persistent HTTP with the browser configured for 6 parallel connections?
    \item[c.] Persistent HTTP?
\end{itemize}

\subsection*{Solution}

    \subsubsection*{a. Non-persistent HTTP with no parallel TCP connections}

    For non-persistent HTTP without parallel connections, each object (including the initial HTML file and the eight small objects) requires a separate TCP connection established sequentially.

    \begin{enumerate}
        \item \textbf{Initial HTML file:}
        \begin{itemize}
            \item \textbf{1 RTT} for the TCP connection establishment (three-way handshake).
            \item \textbf{1 RTT} for the HTTP request and the reception of the HTML file.
        \end{itemize}
        Total time for initial HTML file: \( 1 \text{ RTT} + 1 \text{ RTT} = 2 \text{ RTTs} \).
        
        \item \textbf{Eight small objects:}
        \begin{itemize}
            \item For each object:
                \begin{itemize}
                    \item \textbf{1 RTT} for the TCP connection establishment.
                    \item \textbf{1 RTT} for the HTTP request and response.
                \end{itemize}
            \item Time per object: \( 1 \text{ RTT} + 1 \text{ RTT} = 2 \text{ RTTs} \).
            \item Total time for eight objects: \( 8 \times 2 \text{ RTTs} = 16 \text{ RTTs} \).
        \end{itemize}
    \end{enumerate}

    \noindent \textbf{Total elapsed time:}
    \[
    \text{Total time} = 2 \text{ RTTs (initial file)} + 16 \text{ RTTs (objects)} = \boxed{18 \text{ RTTs}}
    \]

    \subsubsection*{b. Non-persistent HTTP with the browser configured for 6 parallel connections}

    With 6 parallel connections, the browser can fetch up to 6 objects simultaneously.

    \begin{enumerate}
        \item \textbf{Initial HTML file:}
        \begin{itemize}
            \item Same as before: \( 1 \text{ RTT (connection)} + 1 \text{ RTT (request/response)} = 2 \text{ RTTs} \).
        \end{itemize}
        
        \item \textbf{First batch of objects (6 objects):}
        \begin{itemize}
            \item \textbf{1 RTT} for TCP connection establishments (simultaneously for all 6 connections).
            \item \textbf{1 RTT} for HTTP requests and responses (also simultaneous).
            \item Total time for first batch: \( 1 \text{ RTT} + 1 \text{ RTT} = 2 \text{ RTTs} \).
        \end{itemize}
        
        \item \textbf{Second batch of objects (2 objects):}
        \begin{itemize}
            \item After the first batch completes, the browser uses available connections to fetch the remaining 2 objects.
            \item \textbf{1 RTT} for TCP connection establishments.
            \item \textbf{1 RTT} for HTTP requests and responses.
            \item Total time for second batch: \( 1 \text{ RTT} + 1 \text{ RTT} = 2 \text{ RTTs} \).
        \end{itemize}
    \end{enumerate}

    \noindent \textbf{Total elapsed time:}
    \[
    \text{Total time} = 2 \text{ RTTs (initial file)} + 2 \text{ RTTs (first batch)} + 2 \text{ RTTs (second batch)} = \boxed{6 \text{ RTTs}}
    \]

    \subsubsection*{c. Persistent HTTP}

    With persistent HTTP, a single TCP connection is used to transfer the initial HTML file and all subsequent objects.

    \begin{enumerate}
        \item \textbf{TCP Connection Establishment:}
        \begin{itemize}
            \item \textbf{1 RTT} for the initial TCP connection establishment.
        \end{itemize}
        
        \item \textbf{Initial HTML file:}
        \begin{itemize}
            \item \textbf{1 RTT} for the HTTP request and response.
        \end{itemize}
        Total time for initial HTML file: \( 1 \text{ RTT (connection)} + 1 \text{ RTT (request/response)} = 2 \text{ RTTs} \).
        
        \item \textbf{Eight small objects:}
        \begin{itemize}
            \item Since the connection is persistent, no additional RTTs are needed for connection establishments.
            \item Without pipelining (requests are sent one after another):
                \begin{itemize}
                    \item Each object requires \textbf{1 RTT} for its HTTP request and response.
                    \item Total time for eight objects: \( 8 \times 1 \text{ RTT} = 8 \text{ RTTs} \).
                \end{itemize}
        \end{itemize}
    \end{enumerate}

    \noindent \textbf{Total elapsed time:}
    \[
    \text{Total time} = 2 \text{ RTTs (initial file)} + 8 \text{ RTTs (objects)} = \boxed{10 \text{ RTTs}}
    \]

    \noindent \textbf{Note:} If HTTP pipelining were used (allowing multiple requests to be sent without waiting for responses), the eight objects could be requested back-to-back, potentially reducing the time further. However, since pipelining is not specified, we assume it is not used.


\end{document}